Morse Theory

### 2020-12-06 paper.tex
Adding citations for Oceanography

\begin{thebibliography}{9}
     \bibitem{MorseTheory}
     {\sc Hua Amy}
       An introductory treatment of morse theory on manifolds
       \href{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}
     \bibitem{Reebgraphs}
     {\sc Cole-McLaughlin at al.} 
       `` Loops in Reeb Graphs of 2-Manifolds  \href{https://core.ac.uk/download/pdf/20670562.pdf}{https://core.ac.uk/download/pdf/20670562.pdf}
     \bibitem{Mapper}
         {\sc Singh at al. }
          Loops in Reeb Graphs of 2-Manifolds \href{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}
    \bibitem{Textbook}
        {\sc Allan Pollack and Victor Guillemin } 
        Differential Topology
\end{thebibliography}
\end{document}

>>>>

\begin{thebibliography}{9}
     \bibitem{MorseTheory}
     {\sc Hua Amy}
       An introductory treatment of morse theory on manifolds
       \href{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}
     \bibitem{Reebgraphs}
     {\sc Cole-McLaughlin at al.} 
       `` Loops in Reeb Graphs of 2-Manifolds  \href{https://core.ac.uk/download/pdf/20670562.pdf}{https://core.ac.uk/download/pdf/20670562.pdf}
     \bibitem{Mapper}
         {\sc Singh at al. }
          Loops in Reeb Graphs of 2-Manifolds \href{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2010/REUPapers/Hua.pdf}
    \bibitem{Textbook}
        {\sc Allan Pollack and Victor Guillemin } 
        Differential Topology
    \bibitem{NeutralSurface}
        {\sc Trevor J. McDougall}
        Neutral surface topology \href{https://www.sciencedirect.com/science/article/pii/S1463500318302221}{https://www.sciencedirect.com/science/article/pii/S1463500318302221}
    \bibitem{NeutralSurfaceTopology}
        {\sc Geoffrey J. Stanley}
        Neutral Surface Topology \href{https://web.archive.org/web/20170623111023/http://journals.ametsoc.org/doi/abs/10.1175/1520-0485%281987%29017%3C1950%3ANS%3E2.0.CO%3B2}{https://web.archive.org/web/20170623111023/http://journals.ametsoc.org/doi/abs/10.1175/1520-0485}

\end{thebibliography}
\end{document}
